### 2012-07-24 docs/mg/mg.tex
add discussion of the bottom solvers

>>>>

There are several bottom solvers available to \maestro.  These are set
through the {\tt mg\_bottom\_solver} (MAC) and {\tt
  hg\_bottom\_solver} (HG) runtime parameters.  The allowed values
  are:

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 0: smoothing only.

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 1: biconjugate
  gradient stabilized---this is the default.

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 2: conjugate
  gradient method

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 4: a special 
  bottom solver that extends the range of the multigrid coarsening
  by aggregrating coarse grids on the original mesh together and
  further coarsening. \MarginPar{does this option then use bicg 
  at the new bottom?}

\MarginPar{any simple discussion on why we might choose one of the
  other bottom solvers?}
